---
title: "Untitled"
output: html_document
---
libraries 
```{r eval=FALSE}
library(MixSim) #To create the cluster data
library(plyr) #For data editing
library(tidyr) #For data editing
library(NbClust) #30 stopping rules 

```


Define a function, that lets me only input K into MixSim to simulate data with diferent numbers of clusters


K is the number of clusters, p in the dimensions, n is the number of datapoints. 
```{r eval=FALSE}

NbClust2Tibble <- function(K){
  
  coordinates <- MixSim(MaxOmega = 0.00, BarOmega = 0.00, K, p =2, int = c(0.2, 1))
  coordinates <- simdataset(n = 100, Pi = coordinates$Pi, Mu = coordinates$Mu, S = coordinates$S, lambda = c(0.1, 10))
  coordinates <- data.frame(as_tibble(coordinates$X))
  
  return(coordinates=coordinates)
 
}
```



Create a loop, which will create the cluster coordinate with the function above, and pass it to NbClust 
```{r eval=FALSE}
K = c(2:10)
label=data.frame(0)
d = data.frame(0)
result = data.frame(0)


for (i in 1:9){
  
  d <- NbClust2Tibble(K[i]) #Call function to create data 
  label[i] <- data.frame(K[i]) #Save the label to know which amount of clusters were used in each iterations 
  d <-NbClust(d, distance = "euclidean", min.nc = 2, max.nc = 15, method = "complete", index = "alllong") #Use NbClusts 30 rules 
  result <- data.frame(result, d$Best.nc[-2,]) #Save guess for each stopping rule into dataframe, new column for each iteration 
}

```


Create a loop, which will calculate the score for each stopping rule 
```{r eval=FALSE}
score = data.frame(0)
result=data.frame(result[,-1], score)
label <- data.frame(t(K))
result=rename(result, c("X0"="score"))


for (i in 1:nrow(result)){
  for (t in 1:9){
    
    result$score[i] <- ifelse(result[i,t] == label[t], result$score[i] +1, result$score[i] +0) #If guess is equal to label, have a point. 
  }
}


```



A loop that picks a random value of K (between 2 and 15) and tests the stopping rules 
```{r}
K = round(runif(100, min = 2, max = 15),digits = 0  ) #Create 100 random digits between 2 and 15 
label=data.frame(0)
d = data.frame(0)
result = data.frame(0)


for (i in 1:length(K)){
  
  d <- NbClust2Tibble(K[i])
  label[i] <- data.frame(K[i])
  d <-NbClust(d, distance = "euclidean", min.nc = 2, max.nc = 30, method = "complete", index = "alllong")

  result <- data.frame(result, d$Best.nc[-2,])
}

```

Create a loop, which will calculate the score for each stopping rule 
```{r eval=FALSE}
score = data.frame(0)

result=data.frame(result[,-1], score)

label <- data.frame(t(K))

result=rename(result, c("X0"="score"))


for (i in 1:nrow(result)){
  for (t in 1:100){
    
    result$score[i] <- ifelse(result[i,t] == label[t], result$score[i] +1, result$score[i] +0)
  }
}


```




